---
title: "Developing Data Products Week 2 Assignment"
author: "SitiSoraya"
date: "November 19, 2019"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the assignment

This is an R Markdown presentation, that features a map created with Leaflet. Here is a map of Kuala Lumpur, capital city of Malaysia and its adjacent city is Petaling Jaya, Selangor state.

## Decimal latitude and longitude coordinates

- Decimal latitude and longitude coordinates for Kuala Lumpur: 3.1412, 101.68653
- Decimal latitude and longitude coordinates for Petaling Jaya, Selangor: 3.1279, 101.59449

## The output

```{r}
library(leaflet)
my_map <- leaflet() %>%
    addTiles() %>%
    addMarkers(lat=3.1412, lng=101.68653, popup="Kuala Lumpur, Malaysia") %>%
    addMarkers(lat=3.1279, lng=101.59449, popup="Petaling Jaya, Selangor")
my_map
```

## The output (cont.)

```{r}
df <- data.frame(lat=runif(500, min=3.15, max = 3.25),
                 lng=runif(500, min=101.69, max = 101.79))

df %>%
    leaflet() %>%
    addTiles() %>%  
    addMarkers(clusterOptions = markerClusterOptions())
```